\section*{Abstract}
Deep reinforcement learning has arisen to achieve remarkable success in domains such as game playing, robotics, recommendation systems, control, and large-scale decision making\citep{mnih2015human,silver2017mastering}. However, despite these successes, modern deep reinforcement learning systems frequently suffer from a phenomenon known as plasticity loss.

Plasticity in general is the ability of a system to change how it perceives and processes the data and be able to adapt. In the context of human, Neuroplasticity is the brain's remarkable capacity to reorganize, grow, and rewire its neural connections throughout your lifetime. Rather than being a fixed organ, it continuously adapts to new experiences, learning processes, and environmental stimuli, or following an injury. \citep{puderbaugh2023neuroplasticity}. In the context of deep learning though, it refers to a neural network’s ability to adapt its predictions when new information becomes available. As training progresses, networks often become increasingly difficult to modify, resulting in slower learning, reduced adaptability, and performance degradation in non-stationary environments\citep{lyle2023understanding,ash2020warm}.

As we use DRL systems more and more by the day, we need to find the root causes preventing neural networks to benefit from plasticity while solving tasks in the reinforcement learning regime.

The objective of this project is to execute a literature study and investigate the mechanisms responsible for plasticity loss and understand how this phenomenon affects deep reinforcement learning systems. We would also reproduce the results based on the work \citep{lyle2023understanding} and argue about the effect of geometrical landscape of functions and their effect on learning.
